\chapter{Introduction}
\label{ch:Introduction}

\vspace{-1cm}
\begin{center}
Eduard Hirsch, Thomas Heistracher and Paolo Dini
\end{center}


\section{Objectives and Motivation}
The overarching objective of this report is to present the concepts and steps necessary for planning, implementing, and running a demonstrator of the distributed ledger specification  for the Sardex system developed by the INTERLACE project and based on the Abstract State Interaction Machines (ASIMs) \cite{BIOMICSD42,BIOMICSD52}. The ASIMs are a generalization of the Abstract State Machines (ASMs) \cite{BoergerStaerk2003,BoergerRaschke2018} that extends their functionality to support communications between ASIMs running concurrently and asynchronously on different hosts. More specifically, this report provides a consistent view of the Interaction Computing Execution Framework (ICEF), of the CoreASIM executable modelling language, and of the implementation of the INTERLACE business logic in this environment. This first demonstrator implementation reflects the core architectural decisions made for a full-stack environment.

Before addressing the modelling and execution framework and the implementation-related work done, this report also presents a refinement of the requirements laid out in Deliverable D2.1 \cite{INTERLACE_D21} for the purpose of developing a prototypical software implementation. In addition, these refined requirements are also expressed as a formal ASIM specification in the Appendix of this report. The Appendix should be seen as the next iteration of the specification provided in Chapter 3 of D2.1, based on the updated requirements description presented in Chapter \ref{ch:UpdatedBLS} of the present report. The ASIM specification in the Appendix forms the basis for the ICEF-compatible notation used for the actual demonstrator implementation.

The main motivations of the implementation effort are to demonstrate the viability of the underlying Interaction Computing approach and to act as a proof-of-concept for the INTERLACE payment specifications.

\section{Scope and Organization}
Within the scope of this report, the refinements of the business logic specification are derived and explained in Chapter \ref{ch:UpdatedBLS} through a textual description together with illustrations, diagrams, and tables. Chapter \ref{ch:CoreAsimIntro} explains the configuration of the execution environment with all necessary software products and tools, the setup of the ICEF, and the CoreASIM language for implementing executable models. Chapter \ref{ch:CoreAsimImplementation} discusses in detail the main implementation aspects and features in CoreASIM. The report concludes giving guidelines and addressing expected challenges for further development such as testing and increasing stability of the ICEF framework. A more detailed discussion of software testing and of the achieved outcomes will be documented in Deliverable D3.2.


\newpage
